Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

As before, let $R_1, ..., R_{k-2}, H$, and $V$ be the input sets of the H-V $k$-SJ problem. Denote by $\J_1$ the set of type-1 result tuples defined in Section~\ref{sec:hv}. In this section, we aim to compute a set $\J^*$ satisfying
\myeqn{
    \J_1
    \subseteq
    \J^*
    \subseteq
    \J(R_1, ..., R_{k-2}, H, V) \label{eqn:hv:type1:J*}
}
where $\J(R_1, ..., R_{k-2}, H, V)$, let us recall, is the join result of the (whole) H-V $k$-SJ. From $\J^*$, we will report only those $k$-tuples belonging to $\J_1$ and ignore the rest. Remember that $\out$ is the size of $\J(R_1, ..., R_{k-2}, H, V)$.

\extraspacing {\bf The Sets $\bm{R_1', R_2', ..., R'_{k-2}}$.} For each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$ (resp., $h_2$): the lowest (resp., highest) segment --- i.e., with the smallest (resp., largest) y-coordinate --- among all the segments in $H$ that cross $r$;

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle bounded by the above four segments as shown in Figure~\ref{fig:hv:type1:trim} ($r_1'$ is the shaded area). We say that $r_1'$ is the {\em trimmed rectangle} of $r_1$, and conversely, $r_1$ is the {\em full rectangle} of $r_1'$. Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}} \nn
}
which we refer to as the {\em trimmed} version of $R_1$. Computing the ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\mathscr{D}$ (the first-crossing version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time.

@@

\begin{figure}
    \includegraphics[height=30mm]{./artwork/four-segs}
    \figcapup
    \caption{Trimming}
    \label{fig:hv:type1:trim}
    \figcapdown
\end{figure}

>>>>

As before, let $R_1, ..., R_{k-2}, H$, and $V$ be the input sets of the H-V $k$-SJ problem. Denote by $\J_1$ the set of type-1 result tuples defined in Section~\ref{sec:hv}. In this section, we aim to compute a set $\J^*$ satisfying
\myeqn{
    \J_1
    \subseteq
    \J^*
    \subseteq
    \J(R_1, ..., R_{k-2}, H, V) \label{eqn:hv:type1:J*}
}
where $\J(R_1, ..., R_{k-2}, H, V)$, let us recall, is the join result of the (whole) H-V $k$-SJ. Remember that the output size $\out$ is defined to $|\J(R_1, ..., R_{k-2}, H, V)|$. From $\J^*$, we will report only those $k$-tuples belonging to $\J_1$ and ignore the rest.

\extraspacing {\bf Sets $\bm{R_1', R_2', ..., R'_{k-2}}$.} For each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$ (resp., $h_2$): the lowest (resp., highest) segment in $H$ that crosses $r$;

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment in $V$ that crosses $r$.
}
Define $r_1' = [x_1, x_2] \times [y_1, y_2]$, where $x_1$ (resp., $x_2$) is x-coordinate of $v_1$ (resp., $v_2$), and $y_1$ (resp., $y_2$) is y-coordinate of $h_1$ (resp., $h_2$). We say that $r_1'$ is the {\em trimmed rectangle} of $r_1$, and conversely, $r_1$ is the {\em full rectangle} of $r_1'$. Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}} \nn
}
which we call the {\em trimmed} version of $R_1$. Computing the ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\mathscr{D}$ (the find-lowest version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time.

@@

% \begin{figure}
%     \includegraphics[height=30mm]{./artwork/four-segs}
%     \figcapup
%     \caption{Trimming}
%     \label{fig:hv:type1:trim}
%     \figcapdown
% \end{figure}
